\clearpage

\addcontentsline{toc}{chapter}{Bibliography}

%\pagestyle{plain} % Remove all the special formatting in the fancyhdr

\fancyhead[LO]{\textit{Bibliography}}
\fancyhead[RO]{}

\begin{thebibliography}{99}
\raggedright


\bibitem{politifactAbout}
Adair, B., \& Holan, A. D. (2013, November 1). The Principles of PolitiFact, PunditFact and the Truth-O-Meter. Retrieved from \url{http://www.politifact.com/truth-o-meter/article/2013/nov/01/principles-politifact-punditfact-and-truth-o-meter/}

\bibitem{gentzkow}
Allcott, H., \& Gentzkow, M. (2017, January). Social Media and Fake News in the 2016 Election. Retrieved from \url{https://web.stanford.edu/~gentzkow/research/fakenews.pdf}

\bibitem{deepMindHouseNumber}
Ba, J., Minh, V., \& Kavukcuoglu, K. (2015, April 23). Multiple Object Recognition with Visual Attention. Retrieved from \url{https://arxiv.org/pdf/1412.7755.pdf}

\bibitem{rnnUnfolding}
Bengio, Y., Hinton, G., \& LeCun, Y. (2015, September 17). \textit{A Recurrent Neural Network and the Unfolding in Time of the Computation Involved in its Forward Computation} [Digital image]. Retrieved from \url{https://images.nature.com/full/nature-assets/nature/journal/v521/n7553/images/nature14539-f5.jpg}

\bibitem{rbfKernel}
Bernstein, M. (2017, March 28). The Radial Basis Function Kernel. Retrieved from \url{http://pages.cs.wisc.edu/~matthewb/pages/notes/pdf/svms/RBFKernel.pdf}

\bibitem{bishop}
Bishop, C. M. (2006). Kernel Methods, \textit{Pattern Recognition and Machine Learning} (p. 292). New York, NY: Springer.

\bibitem{englandFakeNews}
Booth, W. (2017, November 14). Britain's May Slams Russia For Election Meddling and Fake News (Unlike President Trump). Retrieved from \url{https://www.washingtonpost.com/news/worldviews/wp/2017/11/14/britains-may-slams-russia-for-election-meddling-and-fake-news-unlike-president-trump/}

\bibitem{porterStemmer}
Boulton, R. \& Porter, M. (2001). The Porter Stemming Algorithm. Retrieved from \url{http://snowball.tartarus.org/algorithms/porter/stemmer.html}

\bibitem{introRNN}
Britz, D. (2015, September 17). Introduction to RNNs. Retrieved from \url{http://www.wildml.com/2015/09/recurrent-neural-networks-tutorial-part-1-introduction-to-rnns/}

\bibitem{intoToBiasVariance}
Brownlee, J. (2016, March 18). Gentle Introduction to the Bias-Variance Trade-Off in Machine Learning. Retrieved from \url{https://machinelearningmastery.com/gentle-introduction-to-the-bias-variance-trade-off-in-machine-learning/}

\bibitem{lstmClassification}
Brownlee, J. (2016, July 26). Sequence Classification with LSTM Recurrent Neural Networks in Python with Keras. Retrieved from \url{https://machinelearningmastery.com/sequence-classification-lstm-recurrent-neural-networks-python-keras/}

\bibitem{dropoutRate}
Brownlee, J. (2017, April 28). How to Use Dropout with LSTM Networks for Time Series Forecasting. Retrieved from \url{https://machinelearningmastery.com/use-dropout-lstm-networks-time-series-forecasting/}

\bibitem{batchSize}
Brownlee, J. (2017, May 15). How to use Different Batch Sizes when Training and Predicting with LSTMs. Retrieved from \url{https://machinelearningmastery.com/use-different-batch-sizes-training-predicting-python-keras/}

\bibitem{bagOfWords}
Brownlee, J. (2017, October 9). A Gentle Introduction to the Bag-of-Words Model. Retrieved from \url{https://machinelearningmastery.com/gentle-introduction-bag-words-model/}

\bibitem{microsoftSentiment}
Cabrera, L. Steen, H., \& Wells, J. (2017, September 5). Text Analytics API Version 2.0. Retrieved from \url{https://docs.microsoft.com/en-us/azure/cognitive-services/text-analytics/overview}

\bibitem{trustworthiness}
Dang, V., Dong, X. L., Gabrilovich, Horn, W., Lugaresi, C., Murphy, K., ... Zhang, W.  (2015, September). \textit{Knowledge-Based Trust: Estimating the Trustworthiness of Web Sources}. Retrieved from \url{http://www.vldb.org/pvldb/vol8/p938-dong.pdf}

\bibitem{tsneVisual}
Derksen, L. (2016, October 29). Visualising High-Dimensional Datasets Using PCA and t-SNE in Python. Retrieved from \url{https://medium.com/@luckylwk/visualising-high-dimensional-datasets-using-pca-and-t-sne-in-python-8ef87e7915b}

\bibitem{fakeNewsAuthor}
Dewey, C. (2016, November 17). Facebook Fake-News Writer: 'I Think Donald Trump is in the White House Because of Me'. Retrieved from \url{https://www.washingtonpost.com/news/the-intersect/wp/2016/11/17/facebook-fake-news-writer-i-think-donald-trump-is-in-the-white-house-because-of-me/}

\bibitem{popaccu}
Dong, X. L., Saha, B., \& Srivastava, D. (2012, December 1). Less Is More: Selecting Sources Wisely for Integration. \textit{PVLDB}, 6(2), 37-48. Retrieved from \url{http://www.vldb.org/pvldb/vol6/p37-dong.pdf}

\bibitem{knowledgeFusion}
Dong, X. L., Gabrilovich, E., Heitz, G., Horn, W., Murphy, K., Sun, S., \& Zhang, W.  (2014, September). \textit{From Data Fusion to Knowledge Fusion}. Retrieved from \url{http://www.vldb.org/pvldb/vol7/p881-dong.pdf}

\bibitem{svcDoc}
Fabian, P. (2010, September 28). C-Support Vector Classification.
Retrieved from \url{http://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html}

\bibitem{tsnePython}
Fabisch, A. (2014, February 3). t-distributed Stochastic Neighbor Embedding. Retrieved from \url{http://scikit-learn.org/stable/modules/generated/sklearn.manifold.TSNE.html}

\bibitem{svmTutorial}
Gavrilov, Z. SVM Tutorial. Retrieved from \url{http://web.mit.edu/zoya/www/SVM.pdf}

\bibitem{variousLSTMs}
Greff, K., Koutnik, J., Schmidhuber, J., Srivastava, R. K., \& Steunebrink, B. R. (2015, March 15). LSTM: A Search Space Odyssey. Retrieved from \url{https://arxiv.org/pdf/1503.04069.pdf}

\bibitem{sentimentApp}
Hassan, A., Korashy, H., \& Medhat, W. (2014). Sentiment Analysis Algorithms and Applications: A Survey. Retrieved from \url{https://pdfs.semanticscholar.org/8589/c0ff39d35630a2798cf6d3f58f63d37b1c03.pdf}

\bibitem{kernelIntro}
Johnson, M. (2009, October). A Brief Introduction To Kernel Classifiers. Retrieved from \url{http://cs.brown.edu/courses/cs195-5/fall2009/docs/lecture\_10-27.pdf}

\bibitem{pythonMetrics}
Joly, A. (2014, July 19). sklearn.metrics.precision\_recall\_fscore\_support. Retrieved from \url{http://scikit-learn.org/stable/modules/generated/sklearn.metrics.precision\_recall\_fscore\_support.html}

\bibitem{preprocessing}
Jurafsky, D. \& Martin, J. (2017, August 7). Regular Expressions, Text Normalization, Edit Distance. \textit{Speech and Language Processing}. Retrieved from \url{https://web.stanford.edu/~jurafsky/slp3/2.pdf}

\bibitem{nbSentiment}
Jurafsky, D. \& Martin, J. (2017, August 7). Naive Bayes and Sentiment Classification. \textit{Speech and Language Processing}. Retrieved from \url{https://web.stanford.edu/~jurafsky/slp3/6.pdf}

\bibitem{neuralNetsNLP}
Jurafsky, D. \& Martin, J. (2017, August 7). Neural Networks and Neural
Language Models. \textit{Speech and Language Processing}. Retrieved from \url{https://web.stanford.edu/~jurafsky/slp3/8.pdf}

\bibitem{rnn}
Karpathy, A. (2015, May 21). The Unreasonable Effectiveness of Recurrent Neural Networks. Retrieved from \url{http://karpathy.github.io/2015/05/21/rnn-effectiveness/}

\bibitem{rnnTransformations}
Karpathy, A. (2015, May 21). \textit{RNN Diagrams} [Digital image]. Retrieved from \url{http://karpathy.github.io/assets/rnn/diags.jpeg}

\bibitem{radialSeparation}
Kim, E. (2017, January 1). \textit{Separable in Higher-Dimension} [Digital image]. Retrieved from \url{http://www.eric-kim.net/eric-kim-net/posts/1/imgs/data\_2d\_to\_3d.png}

\bibitem{mccullochPitts}
Kawaguchi, K. (2000, June 17). The McCulloch-Pitts Model of Neuron. Retrieved from \url{http://wwwold.ece.utep.edu/research/webfuzzy/docs/kk-thesis/kk-thesis-html/node12.html}

\bibitem{forensicLinguistics}
Larner, S. (2014). \textit{Forensic Authorship Analysis and the World Wide Web} (pp. 1-11). London, UK: Palgrave Macmillan UK.

\bibitem{fighingFakeNews}
Leong, L. (2017, May 25). Fighting Fake News: How Google, Facebook and Others Are Trying to Stop It. \textit{Techradar}. Retrieved from \url{http://www.techradar.com/news/fighting-fake-news-how-google-facebook-and-more-are-working-to-stop-it}

\bibitem{tfidf}
Liu, E. (2015, November 17). TF-IDF, Term Frequency-Inverse Document Frequency. Retrieved from \url{http://ethen8181.github.io/machine-learning/clustering\_old/tf\_idf/tf\_idf.html}

\bibitem{tsneAbout}
van der Maaten, L. (2017, July 22). t-SNE. Retrieved from \url{http://lvdmaaten.github.io/tsne/}

\bibitem{knnIR}
Manning, C. D., Raghavan, P., \& Sch\"utze, H. (2008). Vector Space Classification. \textit{Introduction to Information Retrieval} (pp. 297-301). New York, NY: Cambridge University Press. Retrieved from \url{https://nlp.stanford.edu/IR-book/pdf/14vcat.pdf}

\bibitem{svmIR}
Manning, C. D., \& Raghavan, P., Sch\"utze, H. (2008). Support Vector Machines and Machine Learning On Documents. \textit{Introduction to Information Retrieval} (pp. 319-325). New York, NY: Cambridge University Press. Retrieved from \url{https://nlp.stanford.edu/IR-book/pdf/15svm.pdf}

\bibitem{stopWord}
Manning, C. D., Raghavan, P., \& Sch\"utze, H. (2008). The Term Vocabulary and Postings Lists. \textit{Introduction to Information Retrieval} (pp. 27-328). New York, NY: Cambridge University Press. Retrieved from \url{https://nlp.stanford.edu/IR-book/pdf/02voc.pdf}

\bibitem{glove}
Manning, C. D., Pennington, J., \& Socher, R. (2014, August). GloVe: Global Vectors for Word Representation. Retrieved from \url{https://nlp.stanford.edu/pubs/glove.pdf}

\bibitem{gloveExplained}
Manning, C. D., Pennington, J., \& Socher, R. (2014, August). GloVe: Global Vectors for Word Representation. Retrieved from \url{https://nlp.stanford.edu/projects/glove/}

\bibitem{comparativeVsSuperlative}
Manning, C. D., Pennington, J., \& Socher, R. (2014, August). \textit{Comparative-Superlative} [Digital image]. Retrieved from \url{https://nlp.stanford.edu/projects/glove/images/comparative\_superlative.jpg}

\bibitem{usingNN}
Nielsen, M. (2017, August 4). Using Neural Nets to Recognize Handwritten Digits. \textit{Neural Networks and Deep Learning}. Retrieved from \url{http://neuralnetworksanddeeplearning.com/chap1.html}

\bibitem{perceptron}
Nielsen, M. (2017, August 4). \textit{Perceptron} [Digital image]. Retrieved from \url{http://neuralnetworksanddeeplearning.com/images/tikz0.png}

\bibitem{wordEmbedding}
Olah, C. (2014, July 7). Deep Learning, NLP, and Representations. Retrieved from \url{http://colah.github.io/posts/2014-07-NLP-RNNs-Representations/}

\bibitem{wordEmbeddingImg}
Olah, C. (2014, July 7). \textit{t-SNE Visualizations of Word Embeddings} [Digital image]. Retrieved from \url{http://colah.github.io/posts/2014-07-NLP-RNNs-Representations/img/Turian-WordTSNE.png}

\bibitem{tsneAxes}
Olah, C. (2015, January 16). Visualizing Representations: Deep Learning and Human Beings. Retrieved from \url{http://colah.github.io/posts/2015-01-Visualizing-Representations/}

\bibitem{lstm}
Olah, C. (2015, August 27). Understanding LSTM Networks. Retrieved from \url{http://colah.github.io/posts/2015-08-Understanding-LSTMs/}

\bibitem{rnnChain}
Olah, C. (2015, August 27). \textit{The Repeating Module in a RNN} [Digital image]. Retrieved from \url{http://colah.github.io/posts/2015-08-Understanding-LSTMs/img/LSTM3-SimpleRNN.png}

\bibitem{lstmChain}
Olah, C. (2015, August 27). \textit{The Repeating Module in a LSTM} [Digital image]. Retrieved from \url{http://colah.github.io/posts/2015-08-Understanding-LSTMs/img/LSTM3-chain.png}

\bibitem{rnnUnrolled}
Olah, C. (2015, August 27). \textit{An Unrolled Recurrent Neural Network} [Digital image]. Retrieved from \url{http://colah.github.io/posts/2015-08-Understanding-LSTMs/img/RNN-unrolled.png}

\bibitem{preprocessing}
Palmer, D. (2012). Text Preprocessing. \textit{Handbook of Natural Language Processing} (pp. 9–30). Boca Raton, FL: CRC Press.

\bibitem{cataloniaFakeNews}
Palmer, E. (2017, November 18). Spain Catalonia: Did Russian 'Fake News' Stir Things Up?. Retrieved from \url{http://www.bbc.com/news/world-europe-41981539}

\bibitem{sentimentAnalysis}
Pang, B., \& Lee, L. (2008, January). Opinion Mining and Sentiment Analysis. \textit{Foundations and Trends in Information Retrieval}, 2, 1-135. Retrieved from \url{http://www.cs.cornell.edu/home/llee/omsa/omsa-published.pdf}

\bibitem{federalistPapers}
Perlroth, N. (2012, January 3). Software Helps Identify Anonymous Writers or Helps Them Stay That Way. Retrieved from \url{https://bits.blogs.nytimes.com/2012/01/03/software-helps-identify-anonymous-writers-or-helps-them-stay-that-way/}

\bibitem{newsweekSputnik}
Porter, T. (2017, September 13). Right-Wing U.S. Sites Spread Russian Fake News, Says Sputnik Whistleblower. Retrieved from \url{http://www.newsweek.com/right-wing-us-news-sites-are-awash-russian-fake-news-says-sputnik-664241}

\bibitem{kernelMethods}
Rai, P. (2011, September 15). Kernel Methods and Nonlinear Classification. Retrieved from \url{https://www.cs.utah.edu/~piyush/teaching/15-9-print.pdf}

\bibitem{lossFunctions}
Rosenberg, D. (2015, February 11). Loss Functions for Regression and Classification. Retrieved from \url{https://davidrosenberg.github.io/ml2015/docs/3a.loss-functions.pdf}

\bibitem{russianBots}
Shane, S. (2017, September 7). The Fake Americans Russia Created to Influence the Election. Retrieved from \url{https://www.nytimes.com/2017/09/07/us/politics/russia-facebook-twitter-election.html}

\bibitem{pewNewsAcrossSocialMedia}
Shearer, E., \& Gottfried, J. (2017, September 7). News Use Across Social Media Platforms 2017. Retrieved from \url{http://www.journalism.org/2017/09/07/news-use-across-social-media-platforms-2017/}

\bibitem{knowledgeGraph}
Singhal, A. (2012, May 16). Introducing the Knowledge Graph: Things, Not Strings. Retrieved from \url{https://googleblog.blogspot.com/2012/05/introducing-knowledge-graph-things-not.html}

\bibitem{politicoHistoryOfFakeNews}
Soll, J. (2016, December 18). The Long and Brutal History of Fake News. Retrieved from \url{http://www.politico.com/magazine/story/2016/12/fake-news-history-long-violent-214535}

\bibitem{neuralNetworks}
Stergiou, C., \& Siganos, D. (1997, May 12). Neural Networks. Retrieved from \url{https://www.doc.ic.ac.uk/~nd/surprise\_96/journal/vol4/cs11/report.html}

\bibitem{fakeNewsDef}
Tavernise, S. (2016, December 6). As Fake News Spreads Lies, More Readers Shrug at the Truth. \textit{The New York Times}. Retrieved from \url{https://www.nytimes.com/2016/12/06/us/fake-news-partisan-republican-democrat.html}

\bibitem{weir}
Weir, W. (2009). \textit{History's Greatest Lies} (pp. 28-34). Beverly, MA: Fair Winds Press.

\bibitem{activationFn}
Yuret, D. (2017, February 8). \textit{Activation Functions} [Digital image]. Retrieved from \url{http://knet.readthedocs.io/en/v0.7.3/\_images/actf.png}

\bibitem{knnGuide}
Zakka, K. (2016, July 13). A Complete Guide to K-Nearest-Neighbors with Applications in Python and R. Retrieved from \url{https://kevinzakka.github.io/2016/07/13/k-nearest-neighbor/}

\bibitem{breakingNewsDrill}
The Drill For Breaking News. Retrieved from \url{http://handbook.reuters.com/?title=The\_Drill\_for\_Breaking\_News}

\bibitem{freebase}
Google (2017, February 10). Freebase Data Dumps. Retrieved from \url{https://developers.google.com/freebase/data}

\bibitem{googleSentiment}
Google (2017, September 19). Natural Language API Basics. Retrieved from \url{https://cloud.google.com/natural-language/docs/basics}

\bibitem{harvardResearch}
Harvard Library. (2017, March 28). Fake News, Misinformation, and Propaganda. Retrieved from \url{https://guides.library.harvard.edu/fake}

\bibitem{kerasLSTM}
Keras Documentation. (2017, October 2). RNN. Retrieved from \url{https://keras.io/layers/recurrent/}

\bibitem{opensources}
OpenSources Group. (2017, February 14). OpenSources. Retrieved from \url{http://www.opensources.co/}

\bibitem{snopesAbout}
Snopes. (2014, May 27). About Snopes.com. Retrieved from \url{https://www.snopes.com/about-snopes/}



\end{thebibliography}
